Paper 1 Analysis

### 2015-10-22 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Better alpha graph.

<<Graphs_all_models_alphas_time, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="Output elasticity ($\\alpha$) for all models.">>=
AllOE %>% 
  mutate(
    xfacet = as.character(
                interaction(Country, factor(flavor, labels = c("QA", "UA")), sep = " - ")
    ),
    yfacet = as.character(
                interaction(factor(nest, labels = c("(ek)l", "kl", "(kl)e", "(le)k")), CSP, sep = " - ")
    )
  ) %>% 
  gather(key = oe_type, value = oe_value, oe1, oe2, oe3) %>%

>>>>

<<Graphs_all_models_alphas_time, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="Output elasticity ($\\alpha$) for all models.">>=
AllOE %>% 
  mutate(
    xfacet = as.character(interaction(Country, factor(flavor, labels = c("QA", "UA")), sep = " - ")),
    xfacet = relevelFactor(factor(xfacet), c("PT - UA", "PT - QA", "UK - UA", "UK - QA")),
    yfacet = as.character(interaction(factor(nest, labels = c("(ek)l", "kl", "(kl)e", "(le)k")), CSP, sep = " - ")),
    yfacet = relevelFactor(factor(yfacet), c("kl - w/ CSP", "kl - w/o CSP", "(kl)e - w/o CSP", "(le)k - w/o CSP", "(ek)l - w/o CSP"))
  ) %>% 
  gather(key = oe_type, value = oe_value, oe1, oe2, oe3) %>%
